### 2020-03-03 ChapterImplementation/chapterImplementation.tex
Updated: Summary of chapters to Conclusion. More Further Work
Fixed: Label for implementation now a label, not ref
Updated: Reference to i3D paper

\chapter{Implementation}
The implementation of AP will be discussed in this section. The following points will be looked at in detail: 
\begin{itemize}
	\item An overview of the system architecture: How the servers are deployed in the cloud and how they communicate with a client; a breakdown of the components of each server; and potential deployments to be investigated in the future.
	\item Aura Implementation
	\item The algorithms used by the servers to implement AP.
	\item The life cycle of a simulated object as a finite state machine (FSM).
	\item The features and implementation details of the visualiser, including a description of its features and future work to be carried out on the visualiser.
\end{itemize}

>>>>

\chapter{Implementation}\label{Implementation}
The implementation of AP will be discussed in this section. The following work is based on the implementation of AP used in \cite{brown2019aura}, however, with many newer additions. We include full details of the implementation of AP to give a complete and whole solution.

The following points will be looked at in detail: 
\begin{itemize}
	\item An overview of the system architecture: How the servers are deployed in the cloud and how they communicate with a client; a breakdown of the components of each server; and potential deployments to be investigated in the future.
	\item Aura Implementation
	\item The algorithms used by the servers to implement AP.
	\item The life cycle of a simulated object as a finite state machine (FSM).
	\item The features and implementation details of the visualiser, including a description of its features and future work to be carried out on the visualiser.
\end{itemize}
